Symbolic Parsing and\\ Automated Music Transcription

### 2021-05-03 main.tex
intro (cleanup)

** DEL ** 
%Parsing produces an analyze of an input word in the form of a parse tree 
%representing the derivation of a grammar.
In case of ambiguity, several analyses, in general an exponential number, 
are possible for the same input word. 
Weighted CFG associate a weight value to each of its derivation trees, 
based on weighted values associated to each production rules, 
and are therefore useful for the compact representation and the ranking of large sets of parse trees.
Moreover, there exist some efficient specialized parsing algorithms~\cite{Huang05kbest}
to compute the $n$ best derivations of a given input word.

The models and algorithms mentioned above deal with finite input alphabets.
Considering infinite alphabets can however be of practical interest, 
for instance when dealing with sequences of timestamped events.
(approach of music transcription by parsing~\cite{MCM19})

%generalizes weighted parsing: 
%finding the best derivation for a weighted grammar.

We propose here some models of weighted recognizers 
%model of weighted CFG 
computing on words over infinite input alphabets %sets of terminal symbol
- but with finite sets of states and transitions rules. 
% non-terminals and production rules).
In their transition rules, input symbols appear as variables (parameters)
and the weight associated to the transition rule is a function of these variables.
%
This approach is close to the one of Symbolic Automata (SA)~\cite{VeanesdAntoniJACM}, 
except that the domain of weight values 
is not restricted to be Boolean, like for the guards in the rules of SA, 
but can be an arbitrary commutative semiring (assuming some restrictions).

The models defined here are finite automata, transducers and pushdown automata with visibly restriction.
%wrt an edit distance
The latter model of these automata computes on nested words~\cite{AlurMadhusudan09nested}, 
a structured format of words parenthesized with markup symbols, 
which can correspond to a linearization of trees.

>>>>

The various approaches to weighted parsing usually assume a finite input alphabet. %models and algorithms 
Considering infinite or large alphabets can however be of practical interest, 
for instance when processing strings in UTF encodings or for vulnerability detection in Web-applications 
(see \eg~\cite{dAntoni21CACM}), for model checking, 
or when dealing with sequences of timestamped events
(like in the approach of~\cite{MCM19} of automated music transcription by parsing).
%generalizes weighted parsing: 
%finding the best derivation for a weighted grammar.

We propose here some models of weighted recognizers 
%model of weighted CFG 
computing on words over infinite input alphabets %sets of terminal symbol
- but with finite sets of states and transitions rules. 
% non-terminals and production rules).
In their transition rules, input symbols appear as variables (parameters)
and the weight associated to the transition rule is a function of these variables.
%
This approach is close to the case of Symbolic Automata (SA)~\cite{VeanesdAntoniJACM}, 
except that the domain for weight values is not restricted to be Boolean, 
like for the guards in the rules of SA, 
but can be an arbitrary commutative semiring (assuming some restrictions).
%
The models defined here are finite automata, transducers and pushdown automata with visibly restriction.
%wrt an edit distance
The latter model of these automata computes on nested words~\cite{AlurMadhusudan09nested}, 
a structured format of words parenthesized with markup symbols, 
which can correspond to a linearization of trees.
